Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-07-18 Latex/journal_v1/V5/pr.tex
add paper

  Minimum delay for eMBB and mMTC &  4msec \\

@@

    Minimum delay for URLLC &  1msec \\

@@

  Minimum delay for mMTC &  7msec \\

@@

   Maximum received power for mMTC &  20 dBM \\ [.5ex]   

@@

    Maximum received power for eMBB and URLLC &  33 dBM \\ [.5ex]   

@@

Assume we have two services of URLLC and mMTC. In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services URLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
The figure \ref{fig:2}, presented that by increasing the priority factor for URLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{mmtcurllc.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput for mMTC and URLLC vs. Priority of URLLC }
  \label{fig:2}
\end{figure}
In figure \ref{fig:3}, the total sum rate of URLLC and mMTC is shown vs. priority of URLLC. It is shown that the proposed method is much better than the baseline scheme. 
\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{sumRatePri.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput of all services vs. Priority of URLLC}
  \label{fig:3}
\end{figure}

>>>>

  Maximum delay for eMBB &  4msec \\

@@

    Maximum delay for URLLC &  1msec \\

@@

  Maximum delay for mMTC &  7msec \\

@@

   Maximum received power for mMTC &  20 dBm \\ [.5ex]   

@@

    Maximum received power for eMBB and URLLC &  33 dBm \\ [.5ex]   

@@

Assume we have two services of URLLC and mMTC. In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services URLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
The figure \ref{fig:2}, presented that by increasing the priority factor for URLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{mmtcurllc.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput for mMTC and URLLC vs. Priority of URLLC }
  \label{fig:2}
\end{figure}
In figure \ref{fig:3}, the total sum rate of URLLC and mMTC is shown vs. priority of URLLC. It is shown that the proposed method is much better than the baseline scheme. 
\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{sumRatePri.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput of all services vs. Priority of URLLC}
  \label{fig:3}
\end{figure}
In figure \ref{fig:4}, the number of activated VNF for two different mean service time of a one eMBB service is depicted vs. mean arrival time. This figure, presented that as the mean arrival rate increases, the number of activated VNF increases. Moreover, the number of activated VNFs for the mean service rate of $\mu = 1.6Mbps$ is less than the number of activated VNFs for mean service rate of $\mu  =  0.8Mbps$.

\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{vnfNum.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Number of activated VNF in each Service vs. Mean Arrival Rate(Mbps)}
  \label{fig:4}
\end{figure}
